---
title: "Ass2"
author: "Amit"
date: "5/13/2017"
output: github_document
---
## R Markdown
# Get the anatomy grey data and create a graph
# take data from two files
```{r}
setwd("/Users/amitweiss/Desktop/ga")
library(igraph)
ga.data <- read.csv('ga_edgelist.csv', header=T, stringsAsFactors=F)
ga.data2 <- read.csv('ga_actors.csv', header=T, stringsAsFactors=F)
g <- graph.data.frame(ga.data,vertices=ga.data2,directed = F)
g
```
# Coloring the graph
# Plot the graph
```{r}
 
V(g)$color <- "blue"
females <- which(V(g)$gender == "F")
V(g)$color[females] <- "black" 
plot(g)


```
# Make one connected graph from the data
```{r}
c <- components(g, mode="strong")
l_comp <- which.max(c$csize)
g2 <- induced.subgraph(g, V(g)[which(c$membership == l_comp)])
plot(g2)
```

# Use betweenness centarilty 
```{r}
bet = betweenness(g2, v = V(g2), directed=F,normalized=T)
bet
vg_names = V(g2)$name
maxBet <- vg_names[which(bet  == max(bet))]
cat("Max Betweenness name: ", maxBet  , ", value: ", max(bet))
```
# Use closeness centarilty 
```{r}
cl = closeness(g2,v = V(g2), normalized=T)
cl
vg_names = V(g2)$name
maxcl <- vg_names[which(cl  == max(cl))]
cat("Max Closeness name: ", maxcl  , ", value: ", max(cl))
```
# Use eigenvector centarilty 
```{r}
eg = evcent(g2, directed=F)$vector
eg
vg_names = V(g2)$name
maxEg <- vg_names[which(eg  == max(eg))]
cat("Max Eigenvector name: ", maxEg  , ", value: ", max(eg))
```

# clustering - cluster fast greedy
# coloring the graph clustring and plot the coloring graph
# find the modularity of the graph
# find the size of the clustering
```{r}
cfg = cluster_fast_greedy(g2, merges = TRUE, modularity = TRUE,
      membership = TRUE, weights = E(g2)$weight)
cat("the modulairty is : ", modularity(cfg))
cat("\nthe size is: ", sizes(cfg),'(5)')


```

```{r}
V(g2)$color <- cfg$membership
V(g2)$size <- 5
plot(cfg, g2)
```


# clustering - cluster edge betweenness
# coloring the graph clustring and plot the coloring graph
# find the modularity of the graph
# find the size of the clustering
```{r}
ceb = cluster_edge_betweenness(g2, weights = E(g2)$weight, directed = FALSE,
  edge.betweenness = TRUE, merges = TRUE, bridges = TRUE,
  modularity = TRUE, membership = TRUE)
cat("the modulairty is : ", modularity(ceb))
cat("\nthe size is: ", sizes(ceb),'(6)')



```
# color the graph
```{r}
V(g2)$color <- ceb$membership
V(g2)$size <- 5
plot(ceb, g2)
```

# connect to facebook api
```{r}
library(devtools)
install_github("Rfacebook", "pablobarbera", subdir="Rfacebook")
require (Rfacebook)
#fb_oauth <- fbOAuth(app_id="262751134188814", app_secret="6b76a6e3639cc94d26ea280c8b477242",extended_permissions = TRUE)


```
# save the fb_oath
```{r}
#save(fb_oauth, file="fb_oauth")
#load("fb_oauth")
```

# get users from facebook(only users who use the application)
# get friends of the users and create "friends network"
# nodes = poeple
# edges = connections between the friends
# the graph contains 17 vertexes

```{r}
token <- 'EAACEdEose0cBAPNu2sjy21iraFeaoyBBap7pMTW4yM4rML48hfsMb29i14s5ebLlPeBTUmg4dTdjjCOhYt5iMfsqB7L2Qiw8HO3B1SdEqjYHH8JvZBg3Upb2gMZAc6dDKNdTcb2ZB4SOZADX9OWCqsvKGIR19ZAbcp7Mpgg9mUO57iThXnJNt'
me <- getUsers("me", token, private_info=TRUE)
me$name
me$hometown
my_friends <- getFriends(token, simplify = TRUE)
head(my_friends$id, n = 1) # get lowest user ID
my_friends_info <- getUsers(my_friends$id, token, private_info = TRUE)
mat <- getNetwork(token, format = "adj.matrix")
singletons <- rowSums(mat)==0 # friends who are friends with me alone
my_graph <- graph.adjacency(mat[!singletons,!singletons],mode = c("undirected"))
my_graph
layout <- layout.drl(my_graph,options=list(simmer.attraction=0))

```
# Plot the firends network
# We can see that there is two groups of friends
```{r}
plot(my_graph, vertex.size=2, 
     #vertex.label=NA, 
     vertex.label.cex=0.5,
     edge.arrow.size=0, edge.curved=TRUE,layout=layout)

```



# Doing the proccess of stage one again 
```{r}
bet = betweenness(my_graph, v = V(my_graph), directed=F,normalized=T)
bet
vg_names = V(my_graph)$name
maxBet <- vg_names[which(bet  == max(bet))]
cat("Max Betweenness name: ", maxBet  , ", value: ", max(bet))
```
```{r}
cl = closeness(my_graph,v = V(my_graph), normalized=T)
cl
vg_names = V(my_graph)$name
maxcl <- vg_names[which(cl  == max(cl))]
cat("Max Closeness name: ", maxcl  , ", value: ", max(cl))
```
```{r}
eg = evcent(my_graph, directed=F)$vector
eg
vg_names = V(my_graph)$name
maxEg <- vg_names[which(eg  == max(eg))]
cat("Max Eigenvector name: ", maxEg  , ", value: ", max(eg))
```
```{r}
cfg = cluster_fast_greedy(my_graph, merges = TRUE, modularity = TRUE,
      membership = TRUE, weights = E(my_graph)$weight)
cat("the modulairty is : ", modularity(cfg))
cat("\nthe size is: ", sizes(cfg),'(2)')
```
```{r}
ceb = cluster_edge_betweenness(my_graph, weights = E(my_graph)$weight, directed = FALSE,
  edge.betweenness = TRUE, merges = TRUE, bridges = TRUE,
  modularity = TRUE, membership = TRUE)
cat("the modulairty is : ", modularity(ceb))
cat("\nthe size is: ", sizes(ceb),'(2)')
```

```


